Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-02-01 Manuscript/manuscript.Rmd
editted manuscript

3. **Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (refered to hereafter simply as $\textit{distance}$), in basepairs, from the center of the bin to the center of the nearest region of a respective genomic annotation region [??? Decide whether to use "annotation" or "feature"] was calculated. The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1-8).

>>>>

3. **Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (refered to hereafter simply as $\textit{distance}$), in basepairs, from the center of the bin to the center of the nearest region defined by a specific genomic annotation [??? Decide whether to use "annotation" or "feature"; !!!go with annotation] was calculated. The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1-8).
